Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidic System

### 2022-12-12 paper-kelompok/main.tex
Minor grammatical revision

% Pendahuluan
\section{Introduction}
The clinical diagnosis of metabolic diseases, such as diabetes mellitus, highly depends on the measurement of glucose in body fluid.
The number of people suffering from diabetes is rising, and there is over 1 in 10 adults are affected worldwide.
By 2045, 780 million people worldwide are predicted to live with diabetes\cite{b1}.
Diabetes patients are at a higher risk of critical health problems than non-diabetic individuals.
As a result, accurate monitoring of blood glucose concentrations in diabetic patients is crucial for real-time diabetes diagnosis.

>>>>

% Pendahuluan
\section{Introduction}
The clinical diagnosis of metabolic diseases, such as diabetes mellitus, highly depends on the measurement of glucose in body fluids.
The number of people suffering from diabetes is rising, and over 1 in 10 adults in the world is affected.
By 2045, 780 million people worldwide are predicted to live with diabetes\cite{b1}.
Diabetes patients are at a higher risk of critical health problems than non-diabetic individuals.
As a result, accurate monitoring of blood glucose concentrations in diabetic patients is crucial for real-time diabetes diagnosis.
